### 2023-02-07 article.tex
Feedback
Progress

% \paragraph{Simple example}

@@

% \paragraph{The first definition paradata}

@@

% \paragraph{Definition of paradata}

@@

% Code is paradata

@@

% \paragraph{Modern forms of paradata}

A recent paper explores the use of paradata to increase the impact of data,
stating that lack of paradata can be seen as 'a drastic constraint'
in the use of data and offer some suggestions to 
make paradata useful for data re(use):
paradata should be comprehensive, comprehensively documented
and friendly to computers \cite{huvila2022improving}.
These suggestions appear to work with code as well,
where these suggestions show up as best practices (such
as \cite{stodden2013best}), some of which
described below.
The lack of computer code is just as much 'a drastic constraint'
in the use of a (computational) scientific experiment.
The clearest effect of its absence is, most obviously,
that a computational experiment cannot be redone 
easily, yet there are wider implications, described below, as well.

% \paragraph{This paper is about computer code}

This paper is about paradata in the context of a computational
experiment in general and uses an example from genetic 
epidemiology in particular.
It is argued that code, being paradata, is as vital as the academic
paper itself, illustrated by the two scientists at the start of 
this chapter. After that, the implications and recommendations
follow.

@@

@@

Code should be distributed in standard ways \cite{peng2006reproducible}.
The standard way to publish code is to use a code hosting website.
There are multiple code hosting websites, 
with GitHub being the most popular one \cite{cosentino2017systematic}.
GitHub is a website where users can create dedicated pages (called 'repositories')
to upload code and interact with it.
The use of such code hosting websites
has increased strongly \cite{russell2018large},
accommodates collaboration \cite{perez2016ten}
and improves transparency \cite{gorgolewski2016practical}.

>>>>

\paragraph{Simple example}

@@

\paragraph{The first use of paradata}

@@

\paragraph{Definition of paradata}

@@

\paragraph{Code is paradata}

@@

\paragraph{Modern forms of paradata}

A recent paper explores the use of paradata to increase the impact of data,
stating that lack of paradata can be seen as 'a drastic constraint'
in the use of data and offer some suggestions to 
make paradata useful for data re(use):
paradata should be comprehensive, documented in a useful 
way (and shaped by the data) and be friendly to computers \cite{huvila2022improving}.
These suggestions appear to work with code as well.
The lack of computer code is just as much 'a drastic constraint'
in the use of a (computational) scientific experiment.
The reasons why paradata in the form of code matters, 
are the same reaons as why paradata matters,
which are data reuse, research reproducibility, 
contextual understanding of disciplinary differences,
Open Science and insights into 
(scientific) knowledge production \cite{huvila2022improving}.
This chapter will focus mostly on the goals of making science
reproducible and code reusable.

@@

% d: Documentation as a Factor for Project Popularity
%
% There exists a clear relationship between the popularity and the documentation effort [62], [64], [65]. 
% cosentino2017systematic

@@

Code should be distributed in standard ways \cite{peng2006reproducible}.
The standard way to publish code is to use a code hosting website.
There are multiple code hosting websites, 
with GitHub being the most popular one \cite{cosentino2017systematic}.
GitHub is a website where users can create dedicated pages (called 'repositories')
to upload code and interact with it.
The use of such code hosting websites
has increased strongly \cite{russell2018large},
accommodates collaboration \cite{perez2016ten}
and improves transparency \cite{gorgolewski2016practical}.
See \cite{cosentino2017systematic} for an extensive overview of
research conducted on GitHub.
